### 2016-04-04 chapters/scenarios.tex
Screenshot added

We applied these steps to a total of 261 folders, containing in total more than 18.800 files, extracting 306 features. The surplus features result from abstract features, that do not have their own folder, but are implizit in the naming. The resulting feature model is arranged in a total of six hierarchical levels. Additionally, 196 constraints limit the possible valid configurations of \textit{Odoo}.

@@

>>>>

We applied these steps to a total of 261 folders, containing in total more than 18.800 files, extracting 306 features. The surplus features result from abstract features, that do not have their own folder, but are implicit in the naming. The resulting feature model is arranged in a total of six hierarchical levels. Additionally, 196 constraints limit the possible valid configurations of \textit{Odoo}.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{img/img-screenshots.png}
	\caption{Screen shots of the questionnaire dialog while configuring Odoo}
	\label{img-screenshots}
\end{figure}
